---
format: html
editor: visual
---

Welcome to AIxR meetup. This forum exists to facilitate conversations about AI w/ R.

Our main activities are [meetings](./meetings.html) and [discussions](./discussion.html).

Want to be notified of our meetings? Please leave your contact info [here](https://docs.google.com/forms/d/e/1FAIpQLSeN4cGMH9kjM9hYmUlfy4sW4YIRUI_uJ4R4-AhX-UwHWWucKA/viewform) and let us know a little about your interest in ggplot2 extension so we can be in touch!



<!-- Note that the extension ecosystem is extensive and other initiatives exist to support extenders, check out some [other resources](./additional-resources.html). -->

```{r, echo = F, warning=F, fig.height=3.5, eval = F}
# download.file("https://upload.wikimedia.org/wikipedia/commons/thumb/5/5a/Ggplot2_hex_logo.png/800px-Ggplot2_hex_logo.png", destfile = "800px-Ggplot2_hex_logo.png")  
  

library(ggstamp)
library(ggplot2)
ggcanvas() + 
  stamp_polygon(x0y0 = pos_honeycomb(n = 50, ncol = 10), 
                fill = "whitesmoke") + 
  ggstamp::stamp_wash(fill = "whitesmoke") +
  ggstamp::theme_void_fill("whitesmoke") + 
  ggstamp::stamp_png(png = "800px-Ggplot2_hex_logo.png", x0 = 6,
                     y0 = -3, width = 4
                    )


```

------------------------------------------------------------------------



### *What people are saying*

```{css, echo = F}
.quote-left {
  width: 80%;
  text-align: left;
  margin: 1em 0;
  padding-left: 1em;
  border-left: 4px solid #ccc;
  background-color: #lightgrey; /* Light blue tint */
  font-style: italic;
  border-radius: 12px;

}

.quote-right {
  width: 80%;
  text-align: right;
  margin: 1em 0 1em 20%;
  padding-right: 1em;
  border-right: 4px solid #ccc;
  background-color: #f0f8ff; /* Light blue tint */
  font-style: italic;
  border-radius: 12px;

}

.wrap-image-left img {
  float: left;
  width: 20%;
  margin: 0 0em 0em 0;
  border-radius: 12px;
}

```




::: quote-left
On Wednesday, I presented on my experiences using LLMs & AI to develop geospatial tools... Kyle Walker on LinkedIn, [Go to  full post ](https://www.linkedin.com/posts/walkerke_developing-r-packages-with-llms-activity-7390078870730878976-bRg8?utm_source=share&utm_medium=member_desktop&rcm=ACoAAAIFK0wBe0Q89iD-ZEWren9Fjl9ugLy3zB0)
:::

::: quote-right

:::

::: quote-left

:::

::: quote-right

:::

::: quote-left

:::

::: quote-right

:::

------------------------------------------------------------------------

### Meeting history [(go to meetings page)](./meetings.html)

```{r, message=F, warning=F, echo = F}
library(tidyverse)

talks <- "meetings.csv" |> 
  read_csv() |> 
  filter(!(date |> str_detect("Soon|Tentative|maybe|TBD"))) |> 
  mutate(date = as.Date(date))
  
```

```{r , fig.width=15, fig.height=15, echo = F, warning=F, message=FALSE}
talks$package <- str_extract(talks$package, "\\{.+\\}")
talks$package[talks$presenter == "Claus Wilke"] <- "Wilke's\n'Fundamentals'"
talks$date[talks$presenter == "Claus Wilke"] <- "2023-01-28"
talks$package[talks$date  == min(talks$date)] <- "First\nMeeting"
talks$package[talks$presenter == "Winston Chang"] <- "R Graphics\nCookbook,ggproto"
# Hassan Kibirige
talks$package[talks$presenter == "Hassan Kibirige"] <- "plotnine"

pos_honeycomb <- function (x0 = 0, y0 = 0, n = 5, ncol = 3, width = 2 * sqrt(0.75), 
    height = width * 0.75/sqrt(0.75)) 
{
    data.frame(x0 = pos_honeycomb_x(x0 = x0, n = n, ncol = ncol, 
        width = width), y0 = pos_honeycomb_y(y0 = y0, n = n, 
        ncol = ncol, height = height))
}


compute_panel_honeycomb <- function(data, scales, ncol = 4){
  
  n <- nrow(data)
  
  pos_honeycomb(n = n, ncol = ncol) %>% 
    mutate(x = x0, y = y0) %>% 
    bind_cols(data)
  
} 

compute_panel_honeycomb_hex <- function(data, scales, n_vertices = 6, radius = .9, rotation = -.5, ncol = 4){

 n <- nrow(data)
 x0y0 <- pos_honeycomb(n = n, ncol = ncol)

 data %>% 
   mutate(id = 1:n) %>% 
   bind_cols(x0y0) %>% 
   crossing(the_n = 1:n_vertices) %>% 
   mutate(x = x0 + radius * cos(-2 * pi * 0:(n_vertices - 1)/n_vertices - rotation * pi), 
          y = y0 + radius * sin(-2 * pi * 0:(n_vertices - 1)/n_vertices - rotation * pi))
    
}

library(statexpress)
library(ggstamp)

my_pal <- c("black", "tomato", "white", "dodgerblue", "black")


ggplot(talks) + 
  aes(label = package) + 
  geom_polygon(stat = qstat_panel(compute_panel_honeycomb_hex, 
                                  default_aes = aes(group = after_stat(id))), 
               ncol = 5,
               fill = alpha("black", 0)) |> 
  ggfx::with_outer_glow(colour = "goldenrod", sigma = 3, expand = 5) + 
  geom_polygon(stat = qstat_panel(compute_panel_honeycomb_hex, 
                                  default_aes = aes(group = after_stat(id))), 
               ncol = 5,
               aes(color = NULL),
               alpha = .85) |>
  ggfx::with_inner_glow(colour = "goldenrod") +
  qlayer(geom = "text",
         stat = qstat_panel(compute_panel_honeycomb), 
         mapping = aes(label = date), 
         size = 6,
         vjust = 3, 
         ncol = 5) +
  geom_text(stat = qstat_panel(compute_panel_honeycomb), 
            lineheight = .8,
            aes(size = case_when(nchar(package) <= 8 ~ 30,
                                 nchar(package)<= 10 ~ 25,
                                 TRUE ~ 14.5) ),
            ncol = 5, 
            vjust = 0) |>
  ggfx::with_shadow(x_offset = I(.1), y_offset = I(-.3)) +
  coord_equal() +
  aes(fill = year(date)) + 
  aes(color = I("whitesmoke")) + 
  scale_colour_gradientn(colours = my_pal) +
  guides(size = "none") +
  # ggstamp::theme_void_fill("whitesmoke") + 
  scale_fill_viridis_c(end = .6) + 
  scale_size(range =  c(6, 12)) + 
  guides(fill = "none")


```

<!-- ### Coordination of this space is generously supported by Posit PBC. ðŸ™ -->
